### 2013-03-26 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
cleaning up spn derivation

equations by solving for the $n^th$ Legendre flux moment in the

@@

equations. To extend these equations to multiple dimensions, gelbard
simple replaced the x-plane spatial derivatives in the reduced set of

@@

known as the $SP_N$. Again, we provide closure to this set of
equations with $\phi_{N+1} = 0$. As a concrete example, we will

@@

@@

    (\frac{4}{15}\Sigma_0 + \frac{1}{3}\Sigma_2) &

@@

@@

consitency with the equations defined on the domain. In addition, we

@@

    (\frac{4}{15}\mathbf{\Sigma}_0 + \frac{1}{3}\mathbf{\Sigma}_2) &

>>>>

equations by solving for the $n^{th}$ Legendre flux moment in the

@@

equations. To extend these equations to multiple dimensions, Gelbard
simply replaced the planar spatial derivatives in the reduced set of

@@

defined as the $SP_N$ equations. Again, we provide closure to this set
of equations with $\phi_{N+1} = 0$. As a concrete example, we will

@@

  {\tiny \begin{bmatrix}

@@

    (\frac{4}{9}\Sigma_0 + \frac{5}{9}\Sigma_2) &

@@

  \end{bmatrix}}\:.

@@

consistency with the equations defined on the domain. In addition, we

@@

    (\frac{4}{9}\mathbf{\Sigma}_0 + \frac{5}{9}\mathbf{\Sigma}_2) &
